\documentclass[12pt,a4paper]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{fancyhdr}

\usepackage{xcolor}
\definecolor{readEra}{HTML}{F0DCC8}

% Set header
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{\thepage}

% Title formatting
\titleformat{\section}{\centering\bfseries\Large}{}{0em}{}

% Document starts here
\begin{document}

\pagecolor{readEra}

\begin{center}
    \textbf{May 2023} \\
    \textbf{B.Tech. (CE/CE(DS)/CSE(AIML))/CE(H)} \\
    \textbf{ENVIRONMENTAL SCIENCES (MC-03/MCH-03)}
\end{center}

\vspace{1em}

% Time and Marks section
\noindent \textbf{Time: 3 hours} \hfill \textbf{Max. Marks: 75}

\vspace{1em}

% Instructions section
\section*{Instructions:}
\begin{enumerate}[label=\arabic*.]
    \item It is compulsory to answer all the questions (1.5 marks each) of Part-A in short.
    \item Answer any four questions from Part-B in detail.
    \item Different sub-parts of a question are to be attempted adjacent to each other.
\end{enumerate}

\vspace{1em}

\section*{\textbf{PART-A}}

\noindent \textbf{1.} \quad Write a short note on the following:

\begin{enumerate}[label=(\alph*)]
    \item Green marketing. (1.5)
    \item Eutrophication. (1.5)
    \item Ocean Thermal Energy Conservation (OTEC). (1.5)
    \item Ecological succession. (1.5)
    \item Biogeographic Zones of India. (1.5)
    \item Hotspot of biodiversity. (1.5)
    \item Endemic species. (1.5)
    \item Sanitary landfills. (1.5)
    \item Sustainable Development. (1.5)
    \item Watershed Management. (1.5)
\end{enumerate}

\vspace{1em}

\section*{\textbf{PART-B}}

\noindent \textbf{2.}
\begin{enumerate}[label=(\alph*)]
    \item How would environmental awareness help to protect our environment, explain briefly? (5)
    \item Write an explanatory note on the multidisciplinary nature of environmental science. Briefly describe, how computer engineering plays an important role in conservation and protection of environmental quality? (10)
\end{enumerate}

\noindent \textbf{3.}
\begin{enumerate}[label=(\alph*)]
    \item Give a detailed account of various impacts of traditional and modern agricultural practices on environment. (7.5)
    \item What are the environmental impacts associated with mineral extraction? Briefly explain the remedial measures to reduce the impacts of mining. (7.5)
\end{enumerate}

\noindent \textbf{4.}
\begin{enumerate}[label=(\alph*)]
    \item Define ecosystem. Give a detailed account of structural and functional attributes of an ecosystem. (10)
    \item Why the concept of food web is more realistic than the concept of food chain? (5)
\end{enumerate}

\noindent \textbf{5.}
\begin{enumerate}[label=(\alph*)]
    \item What do you understand by the term biodiversity? Discuss the concept of biodiversity at different hierarchical levels. (7.5)
    \item Elucidate different approaches of biodiversity conservation along with their merits and demerits. (7.5)
\end{enumerate}

\noindent \textbf{6.}
\begin{enumerate}[label=(\alph*)]
    \item What is water pollution? Briefly explain the effects and various control measures of water pollution. (7.5)
    \item What are wastelands? Give a detailed account of various methods or techniques for reclamation of wastelands. (7.5)
\end{enumerate}

\noindent \textbf{7.} \quad Write a short note on any three of the following:

\begin{enumerate}[label=(\alph*)]
    \item Environmental ethics. (1.5)
    \item Life expectancy. (1.5)
    \item Role of IT in environmental and health. (1.5)
    \item Universal Declaration of Human Rights. (1.5)
\end{enumerate}

\end{document}
